\documentclass{article}
\usepackage{graphicx}
\graphicspath{ {Pictures/} }
% ! clear; pdflatex %

\begin{document}


\begin{titlepage}
    \begin{center}
        \vspace{1cm}

        \Large
        \flushleft\textbf{Cook Book of a Researcher}

        \vspace{1cm}
        \textbf{Keanu Nichols}
        \vspace{1cm}
        \newline
        \vfill
        \vspace{1.5cm}
    \end{center}
\end{titlepage}
%\renewcommand\thesection{\Alph{section}}
\tableofcontents
\newpage


%------------------------------------------------------------------------
% First Receipe
%------------------------------------------------------------------------
\section{Spicy Baked Chicken \& Mashed Potatoes}

Ingredients:

\begin{itemize}
    \item Chicken
    \item Onions
    \item Garlic
    \item Seasoning
    \item Salt
    \item Pepper
    \item Butter
    \item Milk
    \item Paprika
\end{itemize}

Instructions:

Baked Chicken:

\begin{enumerate}
    \item First season the chicken with onions, garlic, salt, paprika and black pepper.
    \item After preheat oven to 350 F
    \item Add hot sauce and seasoning to chicken, make sure both is really covering the chicken
    \item Add to oven with foil on and leave for 30 minutes then take out and flip chicken and put it back in oven
    \item Leave for 30 more minutes
    \item Take out and cut it with knife to ensure it's not read
    \item Set oven to broil and hi and leave for five minutes without foil on
\end{enumerate}

Mashed Potatoes:

\begin{enumerate}
    \item Put pot to boil then add salt when it begins to bubble.
    \item Add potatoes and leave for 25 minutes check stick knife and check if easy to pass through
    \item (Note) If not easy to pass through leave for 10 more minutes
    \item If finished take out and peal potatoes
    \item Crush potatoes and add milk (1/2 cup and warm over for 1 minute), salt, black pepeer and butter (about 50 g butter, it's a bit).

Note: Might want to try with Olive oil next time(might burn so will figure out the workaround)
\end{enumerate}

\newpage

%------------------------------------------------------------------------
% Second Receipe
%------------------------------------------------------------------------

\section{Steak and Roasted Potatoes}

Ingredients:

\begin{itemize}
    \item Salt 4 pinches
    \item Black pepper 3 dashes 
    \item 4 potatoes
    \item Olive oil 
    \item Oregano 
    \item Chili powder go around adding it 
    \item Paprika go around adding it 
\end{itemize}

Instructions:
\begin{enumerate}
    \item Preheat oven to 400 degrees F
    \item Cut up potatoes into cubes and place on tray
    \item e:Do not peel potatoes 
    \item Douce it in olive oil and add salt, black pepper, cover in paprika, oregano and chili powder, then douce it again in olive oil
    \item Place tray into oven and let it bake for 30 mins
    \item Take out tray and mix around potatoes and add back into oven for 30 more minutes
    \item Take out steak and rince it and add it to the plate
    \item Add three pinches of salt, black pepper, paprika and olive oil on both sides
    \item Douce grill in olive oil and spread with napkin
    \item Add steak and cook 4 minutes on one side 
    \item Repeat step 9 and then flip 
    \item For one minute add a clump of butter and spread around on steak and use a clove of garlic to spread around on steak

\end{enumerate}
\newpage

%------------------------------------------------------------------------
% Third Receipe
%------------------------------------------------------------------------

\section{Chicken \& Chips}

Ingredients:

\begin{itemize}
    \item four potatoes
    \item 1 cup of flour
    \item 5 pieces of chicken
    \item black pepper
    \item salt
    \item paprika
    \item seasoning
    \item ketchup
    \item mustard
    \item onions
    \item garlic

\end{itemize}

Instructions:
\begin{enumerate}
    \item Peel potatoes and cut up into fries.
    \item Put in a bowl of water and add salt and let it soak for 30 minutes.
    \item Season chicken (salt, black pepper, paprika, ketchup, mustard, onions, garlic) and let it soak for 2 hours.
    \item Fry fries for at least 3 minutes (Keep longer if necessary).
    \item Make dry batter by combining flour, paprika, salt and blackpper and coat chicken in it.
    \item Fry chicken on one side for four minutes then flip on other side for four minutes then cut with knife tosee if blood flows (Want chicken brown).

\end{enumerate}
\newpage


%------------------------------------------------------------------------
% Fourth Receipe
%------------------------------------------------------------------------

\section{Chicken Alfredo}

Ingredients:

\begin{itemize}
    \item onions
    \item garlic
    \item salt
    \item black pepper
    \item spaghetti
    \item butter
    \item parmesian cheese
    \item heavy cream

\end{itemize}

Instructions:
\begin{enumerate}
    \item Season chicken using salt, black pepper, onions and garlic.
    \item Put pot to boil with water and then add spaghetti and cook for 10 minutes.
    \item Cook chicken and then remove from flame.
    \item Add 80 g of butter and 1 cup of heavy cream and mix together.
    \item Add spghetti and mix around then add chicken.
    \item Add parmesian cheese and mix around (Note if too cremay add regular milk).

\end{enumerate}
\newpage

%------------------------------------------------------------------------
% Fifth Receipe
%------------------------------------------------------------------------

\section{Bolognese Sauce}

Ingredients:

\begin{itemize}
    \item onions
    \item garlic
    \item salt
    \item black pepper
    \item oregano
    \item Pasta Sauce
    \item spghetti
    \item worcestershire sauce
    \item ground beef
\end{itemize}

Instructions:
\begin{enumerate}
    \item First season the ground beef with onions, garlic, salt, black pepper and worcestershire sauce.
    \item Next add water to a pan and wait for it to boil then add spaghetti and leave for 10 minutes then drain.
    \item Also put a pot to heat and then add ground beef and let it marinate in it's juices and then add pasta sauce.
    \item Leave for 40 minutes and then add salt, black pepper and oregano if necessary.
\end{enumerate}

\end{document}


